---
title: "Task 1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require("dplyr")) install.packages("dplyr")
if(!require("purrr")) install.packages("purrr")
if(!require("ggplot2")) install.packages("ggplot2")

library(dplyr)
library(purrr)
library(ggplot2)
```

## Task 1 - (b)
First, I need to

coll_mob80 = read.csv(file = "C:/Users/tsl11/Downloads/predoc_exercise/send/data/coll_mobility_1980.csv", header=TRUE, sep=",", stringsAsFactors=FALSE)

# checking if there is NA values(or, missing values) in par_q5, kq1_cond_parq5
mean(is.na(coll_mob80$par_q5))
mean(is.na(coll_mob80$kq1_par_q5))

coll_mob80 = coll_mob80 %>%
                filter(super_opeid > 0) %>%
                arrange(par_q1) %>%
                mutate(npar_q1 = count * par_q1) %>%
                mutate(nkq5_parq1 = npar_q1*kq5_cond_parq1,
                       cum_npq1 = cumsum(npar_q1)) %>%
                mutate(bin = ntile(cum_npq1, 10))
                
vis_coll80 = coll_mob80 %>%
                group_by(bin) %>%
                summarize(wt_q1 = sum(npar_q1)/sum(count), wt_k5q1 = sum(nkq5_parq1)/sum(count))


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
